\mytitle

### 2015-08-03 MSc_diss.tex
Minor changes

\section{Literature review} \label{sec:lit_review}
\subsubsection{Observational studies}

@@

\subsection{Mean AN concentrations}
mean ANs concentrations: \citep{Reeves2007}, 10 ppt \citep{Roberts1998} 14 ppt
\citep{Atherton1989}
Alkyl nitrate concentrations of 0.8-37 pptv (2-butyl and 2- and 3-pentyl nitrates) in remote marine environments [Atlas, 1988] and approximately 2 ppbv in urban environments [Hanst et al., 1982] have been measured.
\citep{Chuck2002}
The atmospheric mole fraction of MeONO2 ranged from 1.2 to 43 pptv (Fig. 2,Aand B) and 0.8 to 10 pptv for EtONO2 (Fig. 2, D and E). These values lie within the range of concentrations reported in the literature for MeONO2 (0.2 to 50 pptv) and EtONO2 (0.3 to 12.2 pptv) in the remote marine troposphere (2, 8, 9).
\citep{Blake2003}
Pacific Ocean methyl nitrate 50 pptv
\citep{Neuman2012}
approx 1 ppb as difference between NOy and (NOx+PAN+HNO3) is sample closest to the plume center

@@

\citep{Neu2008}

>>>>

\section{Literature review} \label{sec:lit_review}
A lot of work is has been dedicated to measurements of alkyl nitrates in different environments and even more to measurements of ozone. The majority of these studies have been done in a observational-modelling framework.

During/After one of these investigations, namely the SAGA campaign, \citep{Atlas1993} proposed by that the short-chained alkyl nitrates ($C_1$-$C_3$) can be produced not only photochemically through the oxidation of their parent hydrocarbons \citep{Roberts1990}, but also emitted directly from equatorial oceans. This has since been
confirmed by field measurements \citep{Chuck2002,Blake2003,Dalh2005}.

There have been a number of studies of the latitudial and seasonal variations of alkyl nitrates in marine air (Blake et al., 2003), in the Arctic (Swanson et al., 2003) and in the
Antarctic (Beyersdorf et al., 2010)
\subsubsection{Observational studies}

@@

\subsubsection{Mean AN concentrations}
\begin{table}
\begin{tabular}{cccc}
\hline
Observation & $RONO_2$                                  & Comments & Reference \\
\hline
ITOP?       & mean $\Sigma RONO_2$ 10 ppt               &          & \citep{Reeves2007} \\
???         & mean $\Sigma RONO_2$ 14 ppt               &          & \citep{Roberts1998} \\
remote marine environments & 2-butyl and 2- and 3-pentyl: 0.8-37 pptv & &\citep{Atherton1989} [Atlas, 1988]\\
urban environments         & 2-butyl and 2- and 3-pentyl?: approx. 2 ppb & & \citep{Atherton1989} [Hanst et al., 1982] \\
??                         & MeONO2: 1.2 to 43 pptv     &          & \citep{Chuck2002} \\
??                         & EtONO2: 0.8 to 10 pptv     &          & \citep{Chuck2002} \\
remote marine troposphere  & MeONO2: 0.2 to 50 pptv     & in lit. (2, 8, 9) & \citep{Chuck2002} \\
remote marine troposphere  & EtONO2: 0.3 to 12.2 pptv   & in lit. (2, 8, 9) & \citep{Chuck2002} \\
Pacific Ocean              & MeONO2: 50 pptv            &                   & \citep{Blake2003} \\
airborne                   & $\Sigma RONO_2$: approx 1 ppb         & difference between NOy and (NOx+PAN+HNO3) 
                                                                     is sample closest to the plume center & \citep{Neuman2012} \\
\hline
\end{tabular}
\end{table}

@@

The first 3-D chemical transport  model simulations examining the role of methyl and ethyl nitrates in tropospheric ozone chemistry have been conducted by \citep{Neu2008}. In their study, they incorporated methyl and ethyl nitrates in the chemical mechanism of the UCI CTM [Carver et al., 1997] and compared their simulated abundances to observations. To assess  the relative importance of
oceanic alkyl nitrates as a natural source of $NO_x$ in remote regions they evaluated their impact on tropospheric $O_3$ and the oxidative capacity of the atmosphere.
